Depression and suicidality as costly signals of need

### 2021-04-08 Paper.rmd
Dealing with US vs India separately for demographic

The demographic variables were strongly confounded with the Indian sample (younger, lower income, more years of education) vs. the US sample (older, higher income, fewer years of education), which, in turn, were confounded with vignette (responses in the Thwarted marriage vignette differed substantially from those in the other vignettes). We therefore restricted our exploration of the sociodemographic variables to the US sample.

Overall, women participants were more likely to believe and help the victim than men, and younger participants were more likely to believe and help the victim than older participants. The caveats are that the sex differences in *Belief* only emerged for the costly signals, the sex differences in *Action* were quite small (but applied across all signals). We found no significant effects of *Income* or *Education* on *Belief* or *Action* (results not reported). See Figures \@ref(fig:demographicsignal), \@ref(fig:demovignettebelief), and \@ref(fig:demovignetteaction).

>>>>

The demographic variables were strongly confounded with Nationality (Indian was younger, lower income, with more years of education than the US), which, in turn, was confounded with vignette (responses in the Thwarted marriage vignette differed substantially from those in the other vignettes). We therefore conducted our exploration of the sociodemographic variables within Nationalities.

Overall, US women participants were more likely to believe and help the victim than US men, and younger participants were more likely to believe and help the victim than older participants. The caveats are that the sex differences in *Belief* only emerged for the costly signals and the sex differences in *Action* were quite small (but applied across all signals). We found no significant effects of *Income* or *Education* on *Belief* or *Action* (results not reported). See Figures \@ref(fig:demographicsignal), \@ref(fig:demovignettebelief), and \@ref(fig:demovignetteaction).
